---
output: word_document
---

```{r setup, include=FALSE}
# check and load required libraries  
if (!requireNamespace("here", quietly = TRUE)) install.packages("here")
require(here)
if (!requireNamespace("arcgisbinding", quietly = TRUE)) install.packages("arcgisbinding")
require(arcgisbinding)
if (!requireNamespace("RSQLite", quietly = TRUE)) install.packages("RSQLite")
require(RSQLite)
if (!requireNamespace("knitr", quietly = TRUE)) install.packages("knitr")
require(knitr)
if (!requireNamespace("xtable", quietly = TRUE)) install.packages("xtable")
require(xtable)
if (!requireNamespace("flextable", quietly = TRUE)) install.packages("flextable")
require(flextable)
if (!requireNamespace("dplyr", quietly = TRUE)) install.packages("dplyr")
require(dplyr)
if (!requireNamespace("dbplyr", quietly = TRUE)) install.packages("dbplyr")
require(dbplyr)

arc.check_product()

## Network Paths and such
biotics_gdb <- "W:/Heritage/Heritage_Data/Biotics_datasets.gdb"

# open the NHA feature class and select and NHA
nha <- arc.open(here("NHA_newTemplate.gdb","NHA_Core"))
selected_nha <- arc.select(nha, where_clause="SITE_NAME='Town Hill Barren'")
nha_siteName <- selected_nha$SITE_NAME
nha_filename <- gsub(" ", "", nha_siteName, fixed=TRUE)
```

---
title: `r paste(as.character(nha_siteName), "NHA")`
---

Site significance rank: `r paste(as.character(selected_nha$SIG_RANK))`  
NHA Join ID: `r paste(as.character(selected_nha$NHA_JOIN_ID))`  
<br><br><br><br>

# Site Description

Site Description - this should be about a one paragraph description of the site describing its location, size, major habitats, or other descriptive information about the site.  General species info can be placed here (e.g. *"The wetlands at this site provide high quality habitat for a number of species of dragonflies."*), but try to avoid specific talk about individual species.  

This brief description from the NHA geodatabase reads: **`r selected_nha[7]$BRIEF_DESC`**  

<br><br><br><br>

**Enter your site description text in the space between these lines:**

***

*<< enter text here, between these brackets. Please do not delete the brackets!! >>*

***

<br><br><br><br>

Species or natural communities of concern that can be found in this NHA include the following:

```{r species table, echo=FALSE}
## Build the Species Table #########################
# open the related species table and get the rows that match the NHA join id from above
nha_relatedSpecies <- arc.open(here("NHA_newTemplate.gdb","NHA_SpeciesTable"))
selected_nha_relatedSpecies <- arc.select(nha_relatedSpecies) # , where_clause=paste("\"NHD_JOIN_ID\"","=",sQuote(selected_nha$NHA_JOIN_ID),sep=" ")  
selected_nha_relatedSpecies <- selected_nha_relatedSpecies[which(selected_nha_relatedSpecies$NHA_JOIN_ID==selected_nha$NHA_JOIN_ID),] #! consider integrating with the previous line the select statement

SD_speciesTable <- selected_nha_relatedSpecies[c("EO_ID","ELCODE","SNAME","SCOMNAME","ELEMENT_TYPE","G_RANK","S_RANK","S_PROTECTI","PBSSTATUS","LAST_OBS_D","BASIC_EO_R")] # subset to columns that are needed.

SD_speciesTablePrint <- SD_speciesTable[,-c(1:2)]
row.names(SD_speciesTablePrint) <- SD_speciesTable$SNAME

#Print species table for site
STable <- flextable(head(SD_speciesTablePrint))
STable <- fontsize(STable, part="all", size=7)
STable <- italic(STable, j= ~ SNAME, italic=TRUE)
STable <- rotate(STable, rotation = "tbrl", part = "header", align = "center")
STable <- align(STable, align = "center", part = "body")
STable <- height(STable, height = 1, part = "header")
STable
```

```{r select Biotics EO Records, echo=FALSE}
eoid_list <- paste(toString(SD_speciesTable$EO_ID), collapse = ",")  # make a list of EOIDs to get data from
ELCODE_list <- paste(toString(sQuote(unique(SD_speciesTable$ELCODE))), collapse = ",")  # make a list of EOIDs to get data from

ptreps <- arc.open(paste(biotics_gdb,"eo_ptreps",sep="/"))
ptreps_selected <- arc.select(ptreps, fields=c("EO_ID", "SNAME", "EO_DATA", "GEN_DESC","MGMT_COM","GENERL_COM"), where_clause=paste("EO_ID IN (", eoid_list, ")",sep="") )

#generate URLs for each EO at site

URL_EOs <- sapply(seq_along(ptreps_selected$EO_ID), function(x)  paste("https://bioticspa.natureserve.org/biotics/services/page/Eo/",ptreps_selected$EO_ID[x],".html", sep=""))

URL_EOs <- sapply(seq_along(URL_EOs), function(x) paste("(",URL_EOs[x],")", sep=""))
Sname_link <- sapply(seq_along(ptreps_selected$SNAME), function(x) paste("[",ptreps_selected$SNAME[x],"]", sep=""))
Links <- paste(Sname_link, URL_EOs, sep="") 

 #for now, add to the biotics table output

## Information from Biotics
```

<br><br><br><br>

## Information from Biotics

See output below from Biotics, in association with all the EOs at this site. Biotics fields reported include `r names(ptreps_selected)`. Use this to inform both the site description and the threats and conservation recommendations section.  
To learn more about each EO, follow the links provided below to the Biotics page for each EO at this site:  

`r Links`  

<br><br><br><br>

```{r print Biotics info, echo=FALSE}

SD_eodata <- ptreps_selected
SD_eodatap <- c(SD_eodata, sep="--")
do.call(paste, SD_eodatap)

```

# Threats and Conservation Recommendations

This area should include a short, one paragraph description of the overall threats and conservation recommendations for the NHA. This paragraph could include an overview of historic impacts, a general statement about the level of site protection, existing management plans, and known conservation issues. Incorporate information specific to the site overall, as well as to the individual EO's present.

<br><br><br><br>

**Enter your threats and conservation recommendations summary paragraph in the space between these lines:**

***  

*<< enter text here, between these brackets. Please do not delete the brackets!! >>*

***  

<br><br><br><br>

Specific threats and conservation recommendations for the elements present at this site include:

The goal of the list items here should be to create a list of known conservation issues at this site, and what needs to be done to address them. Be as specific as you possibly can--for example, if an EO is generally known to be susceptible to invasive species and there is information in Biotics about particular invasive species known to be present at this site, incorporate the specific information into the bullet. For example:  

* *Aggressive non-native plant species are a particular threat to species is calcareous habitats. Left to spread, these species can crowd out the species of concern, as well as other native plant species. Invasive species known to be present at this site include xxxx, xxxx, xxxx, and xxxx. Monitor for invasive plant species and remove them prior to becoming dominant at this site, if possible. Target pioneer populations of invasive plants for immediate and continued removal. It is much easier and more effective to keep a place invasive-free than to try to repair a heavily infested habitat. Invasive species management should be coordinated by individuals familiar with the rare species as well as the invasive species present. Continual invasive species monitoring and control will likely be necessary.*  

<br><br><br><br>

**Enter your specific threats and conservation recommendations bullets in the space between these lines:**

***  

*<< enter text here, between these brackets. Please do not delete the brackets!! >>*

***  

<br><br><br><br>

## EO-Specific Threats and Conservation Recommendation Info

Included below is species-specific information on general conservation threats and recommendations. This includes:  
<br><br><br><br>

1.  A summary table with the number of EOs that fall into each of the conservation threats/recommendations categories at the site. This table is meant to help you quickly summarize the types of issues that the species present at this site face, for the threats and conservation recommendations summary paragraph.   

2. The text for each species-specific threat and recommendation available in the database. Copy and paste those which are relevant at this site into conservation threats and recommendations bullets.


``` {r EO Threats Database, echo=FALSE}
TRdb <- DBI::dbConnect(RSQLite::SQLite(), "P:/Conservation Programs/Natural Heritage Program/ConservationPlanning/NaturalHeritageAreas/NHA_Tool/ELCODE_TR_test.db") #connect to SQLite DB
#src_dbi(TRdb) #check structure of database

ELCODE_TR <- tbl(TRdb, "ELCODE_threatsrecs_test")
TRtable <- tbl(TRdb, "ThreatsrecsTable_test")

#ensure key column is encoded the same way in both linked tables
ELCODE_TR <- ELCODE_TR %>%  
    mutate(TRID = as.numeric(TRID))

TRtable <- TRtable %>%  
    mutate(TRID = as.numeric(TRID))

#select out subset of records to match species table at selected site
ELCODE_sub <- ELCODE_TR %>% 
  filter(ELCODE %in% SD_speciesTable$ELCODE) %>%
  select(ELCODE, SNAME, TRID)

#join tables and report threats and recs for selected species
Sel_TR <- inner_join(ELCODE_sub, TRtable, copy=TRUE) %>%
  select(SNAME, ThreatRec_Name, Threats, Recs, Citation_Full) %>% collect()
  

#summarize by category of threats/recs and number of species present at site which they apply to

Cat_Count <- Sel_TR %>% add_count(ThreatRec_Name) %>% select(ThreatRec_Name, n)
ThreatCatTable <- flextable(head(Cat_Count))
ThreatCatTable <- autofit(ThreatCatTable)
ThreatCatTable

do.call(paste, Sel_TR)

```

<br><br><br><br>

# References

```{r References, echo=FALSE}

Sel_Citations <- inner_join(ELCODE_sub, TRtable, copy=TRUE) %>%
  select(Citation_Full) %>% collect()
do.call(paste, Sel_Citations)
```
# Location

**Municipalities:** `r selected_nha$Muni`  
**USGS quads:** `r selected_nha$USGS_QUAD`  
**Previous CNHI reference:** `r selected_nha$OLD_SITE_NAME`  
**Associated NHAs:** `r selected_nha$ASSOC_NHA`   
**Overlapping Protected Lands:** `r selected_nha$PROTECTED_LANDS`  

Please cite this Natural Heritage Area as:  
Pennsylvania Natural Heritage Program. `r format(Sys.Date(), "%Y")`. `r as.character(nha_siteName)` NHA. Created on `r format(Sys.Date(), "%d %b %Y")`. Available at: http://www.naturalheritage.state.pa.us/CNHI.aspx

<br><br><br><br>

Are there any issues that you noticed that should be corrected, for this site or the EOs? Please describe **in the space between the lines, below:**

***  

*<< enter text here, between these brackets. Please do not delete the brackets!! >>*

***  

<br><br><br><br>


Do you have pictures of either the site, or the species present at the site? If so, **upload them to the NHA report folder and enter accompanying information, below, between the lines.** Add up to 3 images per site:

***
**Photo one**  
* Photographer Name: <<*enter name here. Please do not delete the brackets!!*>>  
* Photo caption: <<*enter short description of photo here. Please do not delete the brackets!!*>>  
* Photo file name: <<*enter name of photo file uploaded to folder here. Please do not delete the brackets!!*>>  

***

<br><br><br><br>


***
**Photo two**  
* Photographer Name: <<*enter name here. Please do not delete the brackets!!*>>  
* Photo caption: <<*enter short description of photo here. Please do not delete the brackets!!*>>  
* Photo file name: <<*enter name of photo file uploaded to folder here. Please do not delete the brackets!!*>>  
 
***

<br><br><br><br>


***
**Photo three**  
* Photographer Name: <<*enter name here. Please do not delete the brackets!!*>>  
* Photo caption: <<*enter short description of photo here. Please do not delete the brackets!!*>>  
* Photo file name: <<*enter name of photo file uploaded to folder here. Please do not delete the brackets!!*>>  

***

