---
output: word_document
---

# `r paste(as.character(nha_siteName), "NHA")` 
Site significance rank: **`r paste(as.character(selected_nha$SIG_RANK))`**      

NHA Join ID: **`r paste(as.character(selected_nha$NHA_JOIN_ID))`**    


<br><br><br><br>

# Instructions  

This template will collect the written content for this NHA and allow us to transfer all information into a formatted report. Please fill in all boxes as completely as possible, using the information from Biotics, our species-specific threats and recommendations database, and our NHA geodatabases, as well as your own personal expertise. **Please do not delete any of the tags** (which look like this: |TAG|), as those demarcate the beginning and ending of each content section. Please make sure to check automated sections, such as the species table and location information, for accuracy. Make notes of any issues in the form of Word comments. Also, please be sure to upload any pictures you have associated with this site into the NHA report picture folder, FOLDER PATH HERE.  

<br><br><br><br>
  
# Overview of NHA Report Status for this Site  
Please highlight or otherwise indicate the answers to the following questions upon completion of this site report; add details if necessary to your responses, using Word comments:  

* Is the underlying spatial information complete and correct for this site?    **yes    no**    
* Is the species table complete and correct for this site?    **yes    no**  
* Did you have enough information to complete a comprehensive threats and conservation recommendations section for this site?    **yes    no**  
* Is this NHA report content complete and ready to be formatted and published?    **yes    no**  
  
***
  
  
# Site Description

Site Description - this should be about a one paragraph description of the site describing its location, size, major habitats, or other descriptive information about the site.  General species info can be placed here (e.g. *"The wetlands at this site provide high quality habitat for a number of species of dragonflies."*).  
<br><br><br><br>
Paragraphs can be added to supply more detail about each species or group of species at this NHA, if you want. If information is added, try to keep it general and not have a lot of detail about each specific taxon as it will help to keep the sites as current as possible without a lot of ongoing editing-remember, we are going to rely on the factsheets for that purpose.  For example, it would be good to say something like "The dragonflies at this site depend on clean water to breed" as that statement would likely be true even if we added or subtracted species to the list.

This brief description from the NHA geodatabase reads: **`r selected_nha[7]$BRIEF_DESC`**  

<br><br><br><br>

**Enter your site description text in the space between these lines:**

***  
|DESC_B|  
  
*enter text here, between these tags. Please do not delete the tags!! *

|DESC_E|  

***

<br><br><br><br>

Please check the species table below for accuracy. Make a note of any issues, using Word comments.

```{r species table, echo=FALSE}
## Build the Species Table #########################

SD_speciesTablePrint <- SD_speciesTable[,-c(1:2)]
row.names(SD_speciesTablePrint) <- SD_speciesTable$SNAME

#Print species table for site
STable <- flextable(head(SD_speciesTablePrint))
STable <- fontsize(STable, part="all", size=7)
STable <- italic(STable, j= ~ SNAME, italic=TRUE)
STable <- rotate(STable, rotation = "tbrl", part = "header", align = "center")
STable <- align(STable, align = "center", part = "body")
STable <- height(STable, height = 1, part = "header")
STable
```

<br><br><br><br>

## Information from Biotics

See output below from Biotics, in association with all the EOs at this site. Biotics fields reported include `r names(ptreps_selected)`. Use this to inform both the site description and the threats and conservation recommendations section.  
To learn more about each EO, follow the links provided below to the Biotics page for each EO at this site (you may have to copy and paste the links into your browser, once logged into Biotics, to get them to work):  

`r Links`  

<br><br><br><br>

```{r print Biotics info, echo=FALSE}

SD_eodata <- ptreps_selected
SD_eodatap <- c(SD_eodata, sep="--")
do.call(paste, SD_eodatap)

```

# Threats and Conservation Recommendations

This area should include, first, a short, one paragraph description of the overall threats and conservation recommendations for the NHA. This paragraph could include an overview of historic impacts, a general statement about the level of site protection, existing management plans, and known conservation issues. Incorporate information specific to the site overall, as well as to the individual EO's present.

<br><br><br><br>

**Enter your threats and conservation recommendations summary paragraph in the space between these lines:**

***  
|THRRECP_B|  

*enter text here, between these tags. Please do not delete the tags!!*
  
|THRRECP_E|   

***  

<br><br><br><br>

Secondly, this section will contain a bulleted list of known conservation issues at this site, and what needs to be done to address them. Use the pre-generated EO-associated conservation threats and recommendations available below as a starting point. Be as specific as you possibly can--for example, if an EO is generally known to be susceptible to invasive species and there is information in Biotics about particular invasive species known to be present at this site, incorporate the specific information into the pre-written invasive species bullet. For example:  

* *Aggressive non-native plant species are a particular threat to species is calcareous habitats. Invasive species known to be present at this site include xxxx, xxxx, xxxx, and xxxx. Monitor for invasive plant species and remove them prior to becoming dominant at this site, if possible. Target pioneer populations of invasive plants for immediate and continued removal.*  

<br><br><br><br>

**Enter your specific threats and conservation recommendations bullets in the space between these lines. Please use the tagging format *|Bull1_B| bullet text here |Bull1_E|, |Bull2_B| bullet text here |Bull2_E|*, etc. until you have completed all the bullets you need:**

***  
|Bull1_B| *bullet text 1, between these tags, Please do not delete these tags!!* |Bull1_E| 

|Bull2_B| *bullet text 2, between these tags, Please do not delete these tags!!* |Bull2_E|   

|Bull3_B| *bullet text 3, between these tags, Please do not delete these tags!!* |Bull3_E|  

*add as many additional, sequentially numbered and tagged bullets as needed*  


***  

<br><br><br><br>

## EO-Specific Threats and Conservation Recommendation Info

Included below is species-specific information on general conservation threats and recommendations. This includes:  
<br><br><br><br>

1.  A summary table with the number of EOs that fall into each of the conservation threats/recommendations categories at the site. This table is meant to help you quickly summarize the types of issues that the species present at this site face, for the threats and conservation recommendations summary paragraph.   

2. The text for each species-specific threat and recommendation available in the database. Copy and paste those which are relevant at this site into conservation threats and recommendations bullets.


``` {r EO Threats Database, echo=FALSE}

#join tables and report threats and recs for selected species
Sel_TR <- inner_join(ELCODE_sub, TRtable, copy=TRUE) %>%
  select(SNAME, ThreatRec_Name, Threats, Recs, Citation_Full) %>% collect()
  
#summarize by category of threats/recs and number of species present at site which they apply to

Cat_Count <- Sel_TR %>% add_count(ThreatRec_Name) %>% select(ThreatRec_Name, n)
ThreatCatTable <- flextable(head(Cat_Count))
ThreatCatTable <- autofit(ThreatCatTable)
ThreatCatTable

do.call(paste, Sel_TR)

```

<br><br><br><br>

# References  

Below, see the list of references associated with the automated threats and recommendations bullets. Please copy and paste below the references that are associated with bullets which you actually used to write this site report.  

***  
|REF_B|  

*enter text here, between these tags. Please do not delete the tags!!*
  
|REF_E|   

***  

```{r References, echo=FALSE}

Sel_Citations <- inner_join(ELCODE_sub, TRtable, copy=TRUE) %>%
  select(Citation_Full) %>% collect()
do.call(paste, Sel_Citations)
```
# Location  
Please indicate whether the information below is correct. Use Word comments to flag any issues.  

**Municipalities:** `r selected_nha$Muni`  
**USGS quads:** `r selected_nha$USGS_QUAD`  
**Previous CNHI reference:** `r selected_nha$OLD_SITE_NAME`  
**Associated NHAs:** `r selected_nha$ASSOC_NHA`   
**Overlapping Protected Lands:** `r selected_nha$PROTECTED_LANDS`  
**Acreage:** `r signif(selected_nha$Acres, digits=0)` acres

Please cite this Natural Heritage Area as:  
Pennsylvania Natural Heritage Program. `r format(Sys.Date(), "%Y")`. `r as.character(nha_siteName)` NHA. Created on `r format(Sys.Date(), "%d %b %Y")`. Available at: http://www.naturalheritage.state.pa.us/CNHI.aspx

<br><br><br><br>

Do you have pictures of either the site, or the species present at the site? If so, **upload them to the NHA report folder and enter accompanying information, below, between the lines.** Add up to 3 images per site. Please delete any unused photo sections, if you have less than 3 photos:

***
**Photo one**  

1. Photographer Name and affiliation (e.g. Pete Woods, PNHP): |P1N_B| *enter name here.*  |P1N_E|
2. Photo caption: |P1C_B| *enter short description of photo here* |P1C_E|
3. Photo file name: |P1F_B| *enter name of photo file uploaded to folder here, including format (eg.jpg, .png).* |P1F_E|
  
***

<br><br><br><br>


***
 
**Photo two**


1. Photographer Name and affiliation (e.g. Pete Woods, PNHP): |P2N_B| *enter name here.*  |P2N_E|
2. Photo caption: |P2C_B| *enter short description of photo here* |P2C_E|
3. Photo file name: |P2F_B| *enter name of photo file uploaded to folder here, including format (eg.jpg, .png).* |P2F_E|
  

***

<br><br><br><br>


***
 
**Photo three**  

1. Photographer Name and affiliation (e.g. Pete Woods, PNHP): |P3N_B| *enter name here.*  |P3N_E|
2. Photo caption: |P3C_B| *enter short description of photo here* |P3C_E|
3. Photo file name: |P3F_B| *enter name of photo file uploaded to folder here, including format (eg.jpg, .png).* |P3F_E|   
  

***

